PM Mungbean meta-analysis

### 2020-06-22 02_Preliminary_analysis.Rmd
Clarify fungicides used in analysis
Edit for clarity

Amistar Xtra and Custodia are both contain strobilurin and triazole mixes, however, because they contain differing dose ratios (inverted) pooling may not be appropriate.

Perhaps best way forward is to focus the meta-analysis on only the triazoles/DMIs.
This can then be compared to an additional meta-analysis including azoxystrobin as a comparison.

>>>>

Amistar Xtra and Custodia both contain strobilurin and triazole, however, because they contain differing dose ratios (inverted) pooling may not be appropriate.

Perhaps best way forward is to focus the meta-analysis on only the DMIs.
This can then be compared to an additional meta-analysis including azoxystrobin as a comparison.
